---
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## VMO: ShinyApps

The following Shiny Apps were deleveloped for different purposes. Most of them related to personal (or collaborative) research projects or teaching. 

In order get the apps and deploy them locally you need to execute the following code on your R console:

```{r,eval=FALSE}
if (!require('shiny')) install.packages("shiny")
shiny::runGitHub("ShinyApps", "vmoprojs", subdir = "NetCent")
```


Some applications will be deployed in [shinyapps.io](https://www.shinyapps.io/) when need. This feature will be noted in  the description if it is available since my subcription only lets me have 5 apps in the web.


Descriptions of every item are in the next table:

<!-- -   *NetCent*: This App shows the results of the research proyect *A sensitivity measurement of the international trade network in the period 1992-2015* (Una medición de sensibilidad de la red de comercio internacional en el período 1992-2015) developed as a thesis research in [FLACSO](https://www.flacso.edu.ec/) university. [Wilson Pérez-Oviedo](https://www.flacso.edu.ec/portal/docencia/perfil/wilson-perez.1289.1) as well as [John Cajas-Guijarro](https://uce-ec.academia.edu/JohnCajasGuijarro) were research partners in this proyect. -->

| App     | Project                         | Collaborators                | Institution | Description|
|---------|-------------------------------------------|----------------------------|--------------|--------------------------------------|
| *NetCent*(https://vmoprojs.shinyapps.io/NetCent/) | *A sensitivity measurement of the international trade network in the period 1992-2015* | [Wilson Pérez-Oviedo](https://www.flacso.edu.ec/portal/docencia/perfil/wilson-perez.1289.1) and [John Cajas-Guijarro](https://uce-ec.academia.edu/JohnCajasGuijarro) | [FLACSO](https://www.flacso.edu.ec/)      |Time series (1992-2015) of estimated confidence intervals of centrality measures (Country-Country Elasticity and PageRank centrality) through bootstrap are shown. Pairwise Wilcoxon comparisons are also available.|


